---
title: "HW6"
subtitle: "Section 4"
author: "Jiaying Wu"
date: "Due: Friday, December 11"
output: 
  html_document: 
    theme: lumen 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, warning = FALSE)
# knitr::opts_chunk$set(eval = FALSE)
library(dplyr) 
library(readr)
library(ggplot2)
library(broom)
library(NHANES)
library(ggmosaic)
source('ggavplot.R')
# add library statements for other packages you may need
```

# Instructions

This assignment should be submitted on Moodle by **11:59pm CST on Friday, December 11**. You are welcome to work together on the homework; however, what you submit should be *your* words and *your* code, so we recommend writing it up individually. 

To complete your assignment, please follow these steps: 

1. Download `hw6.Rmd` from Moodle and save it some place on your computer that you can easily find again.

2. Make sure that the file you downloaded is called `hw6.Rmd` and not `hw6.Rmd.txt`.

3. Open `hw6.Rmd` in RStudio.

4. Update the section number and author on the third and fourth lines of the file.

5. Make sure you've already installed the `dplyr`, `readr`, `ggplot2`, `broom`, and `mosaic` packages.

6. Try *Knitting* your document: click the `Knit` button at the top of this screen (look for yarn and needle). 

7. Answer the questions in Parts 1--4. Click `Knit` occasionally along the way to make sure everything looks okay.

8. Once you're done with Parts 1--4, click `Knit` one final time. This will turn your R Markdown document into a nicely formatted HTML file. 

9. Look at the HTML file to make sure it looks like you want it to: graphs appearing, no error messages, no data print out that lasts 50 pages, etc.
    
10. Once your HTML file pops up and you've checked that it looks like what you want, click `Open in Browser` and then Print and select "Save as pdf".

11. Turn in two files to Moodle: this `.Rmd` file, and the knitted `.pdf` version you generated in Step 10.




# Part 1. New Project R Code Tasks

This week, we're first going to have you complete model selection and choose your final models, and then you'll work on writing everything up in the final report document. This Rmd will include all of the R code but you will put all of your text in the Final Report Google Doc. 

## Step 1 (Load Data)

Use the code chunk provided below to read your data set into R. *You should use the same dataset you used in HW2--HW5.* Then, perform any transformations and/or filtering that you will need for your regression models. 

```{r load-data}
library(NHANES)
data(NHANES)
head(NHANES)

Adult <- NHANES %>% 
  filter(Age >= 18) %>%
  filter(AgeFirstMarij <= 30 & AgeFirstMarij >= 10) %>%
  filter(!is.na(AgeDecade)) %>%
  filter(!is.na(SmokeAge)) %>%
  filter(!is.na(SmokeNow)) %>%
  filter(!is.na(AgeFirstMarij)) %>%
  filter(!is.na(Education)) %>%
  filter(!is.na(RegularMarij)) %>%
  filter(!is.na(HHIncomeMid)) %>%
  filter(!is.na(Race1)) %>%
  filter(!is.na(Gender))

# create a binary indicator outcome
IndicatorAdult <- 
  Adult %>%
  mutate(AgeFirstMarijAdult = AgeFirstMarij >= 18)  
```



## Step 2 (Add Variables to Linear Regression Model)

Consider your "best" multiple linear regression model from HW3 and think about at least two additional explanatory variables that you would like to add to that model. Fit this larger model. 

```{r fit-larger-linear-model}
#fit a full linear model
lm.mod.full <- 
  Adult %>%
  with(lm(AgeFirstMarij ~ SmokeAge + Education + Gender + Race1 + HHIncome + AgeDecade))
```



## Step 3 (Hypothesis Testing for Linear Regression Coefficients)

Considering this new, larger multiple linear regression model, use hypothesis testing for each individual slope coefficient to consider the evidence you have in support of including those variables in the model. Consider whether some of these variables may not have REAL relationships with the outcome after accounting for the other variables. 

```{r hypothesis-testing-larger-linear-model}
# check hypothsis testing
tidy(lm.mod.full)
```



## Step 4 (Compare Nested Linear Models)

Now fit a model without some of those variables in `lm.mod.full` that may not have REAL relationships after accounting for the other variables. Use a nested hypothesis test to compare `lm.mod.full` with a smaller model, `lm.mod.sub`. The null hypothesis is that the smaller model is correct. Consider whether you have evidence to reject that hypothesis in favor of the full model (`lm.mod.full`). 

```{r compare-nested-linear-models}
# fit a sub model
lm.mod.sub <- 
  Adult %>%
  with(lm(AgeFirstMarij ~ SmokeAge + Education + AgeDecade))

# compare nested linear model
anova(lm.mod.full, lm.mod.sub)
```



## Step 5 (Select a Final Linear Regression Model)

Using the tools available to you (residual plots, R-squared, adjusted R-squared, standard deviation of residuals, hypothesis testing, causal diagrams), fit a variety of models and choose one final model. Be systematic in your process as you'll need to describe your model selection process and justify your final model. (Note: for mastery of the Inference > Model Selection objective (see Final Grading Rubric), you must use at least 3 of these model selection tools.)

```{r compare-linear-models}
# check first model
lm.mod.1 <- 
  Adult %>%
  with(lm(AgeFirstMarij ~ SmokeAge + Education))
tidy(lm.mod.1)
glance(lm.mod.1)

augment(lm.mod.1) %>%
  ggplot(aes(y = .resid, x = .fitted)) + 
  geom_point() + 
  geom_smooth(se = FALSE, color = 'steelblue') + 
  geom_hline(yintercept = 0)

# check second model
lm.mod.2 <- 
  Adult %>%
  with(lm(AgeFirstMarij ~ SmokeAge + AgeDecade))
tidy(lm.mod.2)
glance(lm.mod.2)

augment(lm.mod.2) %>%
  ggplot(aes(y = .resid, x = .fitted)) + 
  geom_point() + 
  geom_smooth(se = FALSE, color = 'steelblue') + 
  geom_hline(yintercept = 0)

# check third model
lm.mod.3 <- 
  Adult %>%
  with(lm(AgeFirstMarij ~ SmokeAge + AgeDecade + Education))
tidy(lm.mod.3)
glance(lm.mod.3)
lm.mod.3 %>%
  ggAVPLOTS

augment(lm.mod.3) %>%
  ggplot(aes(y = .resid, x = .fitted)) + 
  geom_point() + 
  geom_smooth(se = FALSE, color = 'steelblue') + 
  geom_hline(yintercept = 0)

# check fourth model with merged Education
lm.mod.4 <- 
  Adult %>%
  mutate(EducationCut = case_when(
Education %in% c("8th Grade", "9 - 11th Grade", "High School") ~ "High School", 
Education %in% c("Some College", "College Grad") ~ "College" )) %>%
  with(lm(AgeFirstMarij ~ SmokeAge + EducationCut + AgeDecade))
tidy(lm.mod.4)
confint(lm.mod.4)
glance(lm.mod.4)
lm.mod.4 %>%
  ggAVPLOTS

```


```{r final-linear-model}
# fit final linear regression model
final.lm.mod <- 
  Adult %>%
  mutate(EducationCut = case_when(
Education %in% c("8th Grade", "9 - 11th Grade", "High School") ~ "High School", 
Education %in% c("Some College", "College Grad") ~ "College" )) %>%
  with(lm(AgeFirstMarij ~ SmokeAge + EducationCut + AgeDecade))

tidy(final.lm.mod) #you'll need these estimates
confint(final.lm.mod) #you'll need these confidence intervals
glance(final.lm.mod) #you'll need these model evaluation criteria
```



## Step 6 (Add Variables to Logistic Regression Model)

Now consider your multiple logistic regression model from HW4 and think about at least two additional explanatory variables that you would like to add to that model. Fit this larger model. 

```{r fit-larger-logistic-model}
# fit a full model
glm.mod.full <- 
  IndicatorAdult %>%
  with(glm(AgeFirstMarijAdult ~ RegularMarij + SmokeAge + SmokeNow + Gender + Race1 + HHIncome, family = binomial))
```


## Step 7 (Hypothesis Testing for Logistic Regression Coefficients)

Considering this new, larger multiple logistic regression model, use hypothesis testing for each individual slope coefficient to consider the evidence you have in support of including those variables in the model. 

```{r hypothesis-testing-larger-logistic-model}
# check hypothesis testing
tidy(glm.mod.full)
```


## Question 8 (Compare Nested Logistic Models)

Now fit a model without some of those variables in `glm.mod.full` that may not have REAL relationships after accounting for the other variables. Use a nested hypothesis test to compare `glm.mod.full` with a smaller model, `glm.mod.sub`. The null hypothesis is that the smaller model is correct. Consider whether you have evidence to reject that hypothesis in favor of the full model (`glm.mod.full`). 

```{r compare-nested-logistic-models}
# compare nested model with full model
glm.mod.sub <- 
  IndicatorAdult %>%
  with(glm(AgeFirstMarijAdult ~ RegularMarij + SmokeAge + SmokeNow + Gender, family = binomial)) 

anova(glm.mod.full, glm.mod.sub, test='LRT')
```



## Question 9 (Select a Final Logistic Regression Model)

Using the tools available to you (hypothesis testing, causal diagrams, predicted probability boxplots, false positive and false negative rates, accuracy), fit a variety of models and choose one final model. Be systematic in your process as you'll need to describe your model selection process and justify your final model. (Note: for mastery of the Inference > Model Selection objective (see Final Grading Rubric), you must use at least 3 of these model selection tools.)

```{r compare-logistic-models, message=FALSE}
# check first model
glm.mod.1 <- 
  IndicatorAdult %>%
  with(glm(AgeFirstMarijAdult ~ RegularMarij + SmokeNow + SmokeAge + Gender , family = binomial)) 
confint(glm.mod.1) %>% exp() %>% round(2)
tidy(glm.mod.1)

# check second model
glm.mod.2 <- 
  IndicatorAdult %>%
  with(glm(AgeFirstMarijAdult ~ RegularMarij + SmokeNow + Gender, family = binomial)) 
confint(glm.mod.2) %>% exp() %>% round(2)
tidy(glm.mod.2)

glm.mod.2 %>%
  augment(type.predict ='response') %>%
  ggplot(aes(x = factor(AgeFirstMarijAdult), y = .fitted)) +
  geom_boxplot() 

glm.mod.2 %>%
  augment(type.predict ='response') %>%
  mutate(PredictAgeFirstMarijAdult = .fitted >= 0.25) %>%
  count(AgeFirstMarijAdult, PredictAgeFirstMarijAdult) %>% 
  group_by(AgeFirstMarijAdult) %>%
  mutate(prop = n/sum(n)) 

# check third model
glm.mod.3 <- 
  IndicatorAdult %>%
  with(glm(AgeFirstMarijAdult ~ RegularMarij + SmokeAge + Gender, family = binomial)) 
confint(glm.mod.3) %>% exp() %>% round(2)
tidy(glm.mod.3)

glm.mod.3 %>%
  augment(type.predict ='response') %>%
  ggplot(aes(x = factor(AgeFirstMarijAdult), y = .fitted)) +
  geom_boxplot() 

glm.mod.3 %>%
  augment(type.predict ='response') %>%
  mutate(PredictAgeFirstMarijAdult = .fitted >= 0.25) %>%
  count(AgeFirstMarijAdult, PredictAgeFirstMarijAdult) %>% 
  group_by(AgeFirstMarijAdult) %>%
  mutate(prop = n/sum(n)) 

```



```{r final-logistic-model}
# fit final logistic model
final.glm.mod <- 
  IndicatorAdult %>%
  with(glm(AgeFirstMarijAdult ~ RegularMarij + SmokeAge + Gender, family = binomial))

coef(final.glm.mod) %>% exp() #you'll need these estimates
confint(final.glm.mod) %>% exp() #you'll need these confidence intervals

# predicted probability boxplot
augment(final.glm.mod, type.predict = 'response') %>%
  ggplot(aes(x = factor(AgeFirstMarijAdult), y = .fitted)) + #replace ... with outcome variable name
  geom_boxplot() +
  labs(x = 'Outcome', y = 'Predicted Probability of Outcome') + 
  theme_classic()
```


# Part 2. Write Final Project Report Draft

Now that you have selected final linear and logistic regression models, you will write and revise your final project based on the models you selected above and the feedback you received on HW1--HW5.


## Step 1 (Revise Introduction and Limitations)

Based on the feedback you received on HW5, make adjustments and edits to the following sections on your **Final Report Google Doc**:

- Introduction to Topic
- Research Questions
- Introduction to Data
- Limitations



## Step 2 (Update Multiple Linear Regression Section)

### Variable and Sample Descriptions

Considering the final linear regression model you selected above, and reflecting on any feedback you got on HW5, update the following subsections to accurately describe the variables and cases included in that final model (now in paragraph form):

- Variable Descriptions
- Sample Description


### Visualization

Create a visualization that helps address your first research question involving a quantitative outcome. This visualization should include your outcome variable as well as the two explanatory variables that are most relevant to your research question. You do not need to (and should not) include all variables that are involved in your final linear regression model in this visualization; just focus on the primary variables of interest. (If you feel that two visualizations would be more effective, that is ok too.)

```{r visualize-RQ1}
# REPLACE THIS WITH CODE for a plot
# (and numerical summaries, if desired)

Adult %>%
  filter(SmokeAge <= 30) %>%
  mutate(EducationCut = case_when(
Education %in% c("8th Grade", "9 - 11th Grade", "High School") ~ "High School", 
Education %in% c("Some College", "College Grad") ~ "College" )) %>%
  ggplot(aes(x = SmokeAge, y = AgeFirstMarij, color = EducationCut)) +
  geom_point() + 
  geom_smooth(method = 'lm', se = FALSE, formula = y ~ x) + 
  scale_color_viridis_d() +
  xlab("Starting age of Smoking Cigarette") +
  ylab("Starting age of Smoking Marijuana") +
  labs(title = "Marjuana Smoking Behavior with Smoking and Educational Background") +
  labs(fills = "Edcuation Backgrounds") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.1)) +
  theme(text = element_text(family="Times New Roman", face="bold", size=10)) + 
  scale_fill_viridis_d()

glance(final.lm.mod)
tidy(final.lm.mod)
confint(final.lm.mod)

```

Save this visual and upload it (right click - copy and paste) to your **Final Report Google Doc**. Then, in a brief paragraph, thoroughly describe what information you gain from that visualization. You may use numerical summaries in your paragraph to fully describe your visualization. 


### Model Selection

Update your *Model Selection* section to describe the process you implemented in Part 1 to select your final model: what models did you consider? what tools did you use to select your final model? Explain and justify your process.


### Model Statement

Update the equation in the *Model Statement* section to accurately reflect the **final model** you selected in Part 1. Use shortened descriptive variable names (not R variable names) so that someone who has never seen your dataset can understand it.


### Fitted Model

Use the code chunk below to print out the estimates, standard errors, p-values, and 95% confidence intervals for each of the coefficients in your final model.

```{r final-fitted-linear-model}
#you should have fit final.lm.mod in Part 1

tidy(final.lm.mod) # estimates, standard errors, p-values
confint(final.lm.mod) # confidence intervals
```

Then, add these estimates, standard errors, and confidence intervals to the table in the *Fitted Model* section of your Final Report Google Doc. 


### Interpretations

In the *Interpretations* section of your Final Report Google Doc, write a paragraph describing what you learn from the model. In this paragraph, you should interpret the estimate, 95% confidence interval, and p-value for *only the coefficient(s) of interest* (the coefficient(s) that are most relevant to your research question). Make sure to provide a takeaway message describing what you learn from this model with respect to answering your research question.


### Model Evaluation

Use the code chunk below to check whether your final linear regression model meets all linear model conditions and to assess the "goodness" of your final model. 

```{r evaluate-final-linear-model}
# REPLACE THIS WITH CODE to check conditions
augment(final.lm.mod) %>%
  ggplot(aes(y = .resid, x = .fitted)) + 
  geom_point() + 
  geom_smooth(se = FALSE, color = 'steelblue') + 
  geom_hline(yintercept = 0) +  
  xlab('Predicted Starting Smoking Marijuana Age') +
  ylab('Residuals') +
  labs(title = 'Residual Model') +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(family="Times New Roman", face="bold", size=12))

final.lm.mod %>% ggAVPLOTS() 

glance(final.lm.mod) # to evaluate goodness
```

Add any graphical evidence and numerical evidence that you produced above to your Final Report Google Doc. Then, in paragraph form, describe what you've learned about model conditions (straight enough, equal spread, no extreme outliers) and goodness (R-squared, residual standard error, redundancy), putting your conclusions in context.



## Step 3 (Update Multiple Logistic Regression Section)

### Variable and Sample Descriptions

Considering the final *logistic* regression model you selected in Part 1, and reflecting on any feedback you got on HW5, update the following subsections to accurately describe (in paragraph form now) the variables and cases included in that final model:

- Variable Descriptions
- Sample Description


### Visualization

Create a visualization that helps address your second research question involving a binary outcome. This visualization should include your outcome variable as well as the two explanatory variables that are most relevant to your research question. As above, you do not need to (and should not) include all variables that are involved in your final logistic regression model in this visualization; just focus on the primary variables of interest. (If you feel that two visualizations would be more effective, that is ok too.)

```{r visualize-RQ2}
IndicatorAdult %>%
  mutate(smokeAgeCut = cut(SmokeAge, 4)) %>%
  ggplot(aes(x = RegularMarij, y = AgeFirstMarijAdult)) +
  geom_mosaic(aes(x = product(AgeFirstMarijAdult, RegularMarij),fill = AgeFirstMarijAdult)) +
  facet_wrap(~ smokeAgeCut, ncol = 4) +
  theme_minimal() +
  xlab("Current Regularly Smoking Marijuana") +
  ylab('First Time Smoking Marijuana as Adult or Minors') +
  labs(title = "Marijuana Smoking Behavior and Other Smoking Status") +
  labs(fill = 'Start Smoking as Adult')+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(family = "Times New Roman", face = "bold", size = 10))
```

1-3: decrease 
4: later in life, for other reasons

Save this visual and upload it (right click -- copy and paste) to your **Final Report Google Doc**. Then, in a brief paragraph, thoroughly describe what information you gain from that visualization. You may use numerical summaries in your paragraph to fully describe your visualization. 


### Model Selection

Update your *Model Selection* section to describe the process you implemented in Part 1 to select your final model: what models did you consider? what tools did you use to select your final model? Explain and justify your process.


### Model Statement

Update the equation in the *Model Statement* section to accurately reflect the final model you selected in Part 1. Use descriptive variable names so that someone who has never seen your dataset can understand.


### Fitted Model

Use the code chunk below to print out the exponentiated estimates, p-values, and 95% confidence intervals for each of the coefficients in your final model. 

```{r final-fitted-logistic-model}
# should have fit final.glm.mod in Part 1

coef(final.glm.mod) %>% exp() # exp estimates
confint(final.glm.mod) %>% exp() # confidence intervals
tidy(final.glm.mod) # p-values
```

Then, add these estimates, standard errors, and confidence intervals to the table in the *Fitted Model* section of your Final Report Google Doc. 


### Interpretations

In the *Interpretations* section of your Final Report Google Doc, write a paragraph describing what you learn from the model. In this paragraph, you should interpret the exponentiated estimate, exponentiated 95% confidence interval, and p-value for *only the coefficient(s) of interest* (the coefficient(s) that are most relevant to your research question). Make sure to provide a takeaway message describing what you learn from this model with respect to answering your research question.


### Model Evaluation

Use the code chunk below to assess the "goodness" of your final model. 

```{r evaluate-final-logistic-model}
augment(final.glm.mod, type.predict = 'response') %>%
  ggplot(aes(x = factor(AgeFirstMarijAdult), y = .fitted)) + #replace ... with outcome variable name
  geom_boxplot() +
  labs(x = 'Outcome', y = 'Predicted Probability of Outcome') + 
  theme_classic() +
  ylab("Predicted probability of Age Starting Smoking Marijuana as Adult") +
  xlab("Actual probability of Age Starting Smoking Marijuana as Adult (False = Below 18, Ture = Over 18)") +
  labs(title = "Predicted Probabilities v. True Outcome Value") +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme(text = element_text(family = "Times New Roman", face = "bold", size = 10))

# evaluate goodness
threshold <- 0.28

augment(final.glm.mod, type.predict = 'response') %>%  
  mutate(PredictOutcome = .fitted > threshold) %>%
  count(AgeFirstMarijAdult, PredictOutcome) %>% #replace ... with outcome variable name
  group_by(AgeFirstMarijAdult) %>% #replace ... with outcome variable name
  mutate(prop = n/sum(n))
```

Add any graphical evidence and numerical evidence that you produced above to your Final Report Google Doc. Then, in paragraph form, describe what you've learned about model goodness (accuracy, sensitivity, specificity, false positive rate, false negative rate), putting your conclusions in context.



## Step 4 (Conclusion Notes)

Add notes to the *General Takeaways* section of the Conclusion:

- what are the take-aways from your final linear regression model? what have you learned about your first research question?
- what are the take-aways from your final logistic regression model? what have you learned about your second research question?

Then, add notes to the *Limitations* section of the Conclusion:

- what are the limitations of your final linear regression model?
- what are the limitations of your final logistic regression model? 




# Part 3. Self-reflection

After you have finished the assignment, take 5 minutes to think and 20 minutes to free-write in reaction to the following two prompts. You do not need to answer every question listed below, but use these questions to guide your writing. Use this opportunity to reflect on the whole course.

  * Evaluate your course engagement with respect to the provided rubric. Do you think it meets expectations? What have you been doing to create a positive learning environment this module? 
  
  * Evaluate your project work with respect to the provided rubric. Do you think it meets expectations? Do you feel as though you mastered any of the learning objectives yet? 
  

> About the course engagement, I have completed all checkpoints, but there is one checkpoint that I did not get a hundred percent. For many checkpoints, I needed several times to get the right answer. But I have tried to figure out those parts I did not understand when I first attempted and tried my best to go back to these questions every time before the quiz to see if I fully understand the concept. For the group activity, I showed up every class to participate in group activities. I am really proud that I have tried all roles in small group activities. I love being the presenter or being the recorder, but I don't think I'm the best recorder as my typing speed is not as fast as some other classmates. However, I also try to be the recorder from time to time to challenge myself. For the Q&A, I often go to the office every week, both professor's office hours and protectors of this hour to ask questions that I did not understand in recorded videos and from homework. I love going to office hours as I feel the supports from Brianna and preceptors, and I could learn a lot by asking one-one questions. Moreover, I have both asked questions and answered a couple of others' questions on Slack. Sometimes, I use emojis to show my appreciation for others' questions and the professor's answer as it is so important to connect with others during the quarantine. I appreciate asking and answering questions on slack as it is promptly and helps me feel that we are on the same page. For the reflection part, I still remember the first homework. I did not get an 'A' in the reflection part as I did not fully reflect on what I did this week, both in-class activities and homework. But, after reflecting on this mistake, I achieved a good grade for my reflection later and actually get used to reflecting on my performance for a week now. I wouldn't say I reflect on every single point of the week, but I reflect on most parts that are significant to mention or made me feel supportive or challenged. Lastly, for the community, I participate in every class this model and try to open my camera to see classmates in the class. Also, I try to connect with my check-in partner through zoom or sometimes through a short chat in Slack if we're both busy with homework. I still think that I received enough support from others in this class, and tried to give back this positive supports to this community too.

> Regarding my project work, I have mastered making an R markdown file. I feel comfortable coding in R and understand what is a good style and the general good quality of writing here. I think in general I feel comfortable writing the data contact and quality. Something very important for me in this part is to understand what is this question asking from and what I need to answer. And I love doing visualization as I think visualization helps me to understand the research question before even making a model. And I like putting extra effort in visualization as changing the font, changing the color, or try different kinds of visualization to find the best way to show the data. In general, I feel more comfortable interpreting the linear regression model compared to the logistic regression model. But I still don't think I have mastered standard interpretation for both of them, because sometimes it will be hard for me to write in my second language to interpret something that has many technologies. I need some time to understand and paraphrase my sentences. I would like to learn more about interpreting a slope or intercept or anything related in future classes. And in terms of model evaluation, I think I'm fine with that. But sometimes it will be hard for me to make a conclusion which extends a real life situation from my research question. Also, it is still a little bit hard for me to interpret the confidence interval as I understand what it means, but feels hard to write them in words especially for logistical models. I think I'm trying hard to interpret it via spending more time, re-read for a couple of times, and compare with answer keys. I would like to receive more feedback on my confidence interval interpretation from homework six and my final project. In general, I enjoy this course and learned a lot. I think this is the class that I learn the most in MAC. But there's something more that I would like to explore in the future. For example, how to predict certain data or behavior from a model instead of only draw an associated conclusion. 



# Part 4. Partner Check in

During this time of social distancing, we need to be proactive in initiating and maintaining connections with others. To that end, you will be paired with another student in the class to do an informal weekly check-in with each other. You may do this over email or Zoom, and it doesn't need to be long. This provides you an opportunity to connect with someone and support one another during this time. 

**Suggestions: discuss your plans for spring semester and the biggest things you learned about your learning this module, make a plan to read each other's report if you'd like** 

All you need to report here is whether or not you were able to connect with your partner. If this starting to feel like a burden, let me know. 

> "Checked In" 


